\Title

### 2021-01-08 manuscript/manuscript.tex
Elaborate on the caption of figure about depths

It is widely known from potential theory that the depth of a point source
influences the wavelength of the observed field at the surface.
This makes the source depth a key parameter affecting the outcome of
interpolation and other operations done with equivalent sources.
Several different strategies for assigning the depths of equivalent sources
have been proposed in the literature.

\begin{enumerate}
  \item
The simplest option is to locate all sources at the same depth, which we will
call \emph{constant depth} in the future (see Fig.~\ref{fig:depth-types}(a)).
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.
 \item
One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.
 \item
In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth-types}(c)).

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Depth types for locating point sources. We put one source beneath each
        observation point (station) using:
        (a)~a \emph{constant depth} where all sources are located at the same
           depth,
        (b)~a \emph{relative depth} where all sources are located at the same
           vertical distance from its corresponding observation point, and
        (c)~a \emph{variable depth} where the depth of the sources is
           proportional to the average distance to its neighbour sources.
           Notice how the clustered sources on (c) are relatively shallower
           than the
           other ones.
    }
    \label{fig:depth-types}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Examples of different strategies for assigning depths to equivalent
        sources.
        Here we assign one source for each
        observation point, located at the same horizontal coordinates as the
        data points.
        Source depths are
        (a)~a \emph{constant depth} at a chosen vertical coordinate,
        (b)~a \emph{relative depth} determined by uniformly shifting the
        vertical coordinate of data points downwards,
        and
        (c)~a \emph{variable depth} determined by shifting the vertical
        coordinates of the observation points by an amount proportional to the
        average distance to neighbouring sources.
        The distance between data points and their respective sources (a)
        depends on observation height, (b) is constant, and (c) is proportional
        to the horizontal distribution of sources.
        Notice how the closely spaced sources in the middle of the profile (c)
        are shallower than their counterparts in (b).
    }
    \label{fig:depth_types}
\end{figure*}

It is widely known from potential theory that the depth of a point source
influences the wavelength of the observed field at the surface.
This makes the source depth a key parameter affecting the outcome of
interpolation and other operations done with equivalent sources.
Several different strategies for assigning the depths of equivalent sources
have been proposed in the literature.
Here, we will highlight the following (Fig.~\ref{fig:depth_types}):

\begin{enumerate}
  \item
    \emph{Constant depth}:
    The simplest option is to locate all sources at the same depth
    (Fig.~\ref{fig:depth_types}a).
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.
 \item
    \emph{Relative depth}:
One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth_types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.
 \item
    \emph{Variable depth}:
In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth_types}(c)).

@@
